---
title: "Rate_Analysis"
author: "dh"
date: "3 June 2019"
output: word_document
---
---
title: "Experimental Analysis"
output: html_notebook
---

R Notebook for calculating precipitation rate from experimental data.

The first chunk loads the required packages and uses the CalcStat function to load all data from the data_path and then perform a series of calculations to determine precipitation rate in mol/m2/h
```{r}
library(tidyverse)
library(here)
library(cowplot)
library(Cairo)

source("Func_Rate_Calc.R")

SpecificSA <- 0.205 # m2/g
Series <- "Trial_Series"
data_path <- here::here(paste0("pH_Stat/Data/Filtered/", Series))

# Calculate rates
data <- CalcStat(data_path)

# Write to rate_data.csv
write.csv(data[["rate_data"]],
          file=here::here(paste0("pH_Stat/Output/",Series,"/rate_data.csv")),
          row.names = FALSE)

```

This chunk creates stacked plots of pH, titrant volume added, and log rate for the raw data and data which has had the first 1 h trimmed.
```{r}

tri_plot(data[["raw_data"]], here::here(paste0("pH_Stat/Figs/", Series, "/Raw")))

tri_plot(data[["trim_data"]], here::here(paste0("pH_Stat/Figs/", Series, "/Trimmed")))

```


```{r}
#Preliminary plotting
Alkalinity <- read_csv(here::here(paste0("Autotitrator/Output/", Series ,"/alkalinity_data.csv")))
Rate <- data[["rate_data"]]
Combined <- full_join(Alkalinity, Rate, by = "Key")

plotcomp <- ggplot(data = filter(Combined)) +
  geom_point(aes(x = Alk_meq_L_mean, y = log_Rate_mol_m2_h, colour = Designation), size = 3.5) +
  geom_errorbarh(aes(y = log_Rate_mol_m2_h, xmax = Alk_meq_L_mean + Alk_meq_L_sd, xmin = Alk_meq_L_mean - Alk_meq_L_sd))+
  theme_bw()+
  scale_colour_manual("Titr Conc", values = DH_Cols) +
  theme(aspect.ratio = 1) +
  labs(
    x = bquote("Alk (meq/L)"),
    y = expression(paste("Log Rate" ~ "(mol", ~ "m"^{-2}, ~ "h"^{"-1"}, ")"))
  );plotcomp

 ggsave(filename = "Series_Plot.png", plotcomp, path = here::here(paste0("pH_Stat/Figs/", Series)),dpi = 300, width = 15, height = 10, units = "cm", type = "cairo")
```


